Title

### 2013-01-14 inc/extension/initial_conditions/initial_conditions.tex
more work on initial conditions

% longitudinal
In the longitudinal direction ($z$), the interplay between acceleration, $ a = e E_{DC}/m $, in the DC gun and the physics of the photoemission process determine the properties of the electron bunch.
Two limiting regimes for the initial longitudinal variances $ \sigma_{i} ( 0 ) $ are readily identified: (i) by the incident drive laser pulse duration is sufficently long to ensure that the distance the electrons travel due to acceleration in $ E_{DC} $ over the laser pulse duration is much greater than that traveled by electrons with the maximum photoemission velocity $ v_{max} $ alone over the same time period; and (ii) the opposite regime for sufficiently short laser pulse durations.

@@

% v_0 dominated
with the velocity of the pulse in the lab frame $v_{{ \scriptscriptstyle 0}} = \sqrt{ 2 e V / m_{e} d } $, where $ V $ and $ d $ are the potential and cathode-anode separation of the gun's DC acceleration region respectively.
Immediately after photo-generation, however, it is strictly inaccurate to say that $ \gamma_{ z } ( 0 ) = 0 $.
This is because the excess photoemission energy $ \Delta E = \hbar \omega - \Phi $, associated with the electron emission from a material with work function $\Phi$ using photons of energy $ \hbar \omega $ (which gives the maximum initial velocity of an electron, $ v_{max} = \sqrt{ 2 \Delta E/m_{e} } $), can produce an initial momentum chirp.
Nonetheless, the initial non-zero nature of $ \gamma_{z} $ is quickly dominated by the evolution of the pulse, so this approximation will suffice in the region far from the gun.

These initial conditions at $t=0$ for an incident Gaussian laser pulse of the form given in \ref{eq:laser_form}, will be used for the remainder of this paper.
\begin{subequations} \label{eq:summary}
  \begin{gather}
    \sigma_{ \smallT } ( 0 ) = \frac{ w^{ 2 } }{ 2 } \\
    \sigma_{ z } ( 0 ) = \frac{ ( v_{ max } \tau )^{ 2 } }{ 2 } + \left ( \frac{ e E_{ DC } \tau^{ 2 } }{ 4 m } \right )^{ 2 } \\
    \gamma_{ \smallT } ( 0 ) = 0 \\
    \gamma_{ z } ( 0 ) = \sqrt{ \sigma_{ z } ( 0 ) } \left ( 0.06 m v_{ max } + \frac{ e E_{DC} \tau }{ \sqrt{ 2 } } \right ) \\
    \eta_{ \smallT } ( 0 ) = \frac{ m \epsilon_{ F } ( \hbar \omega - \Phi ) }{ 3 ( \hbar \omega + \epsilon_{ F } ) } \\
    \eta_{ z } ( 0 ) = \frac{ \eta_{ \smallT } ( 0 ) }{ 3.85 }
  \end{gather}
\end{subequations}

>>>>

% longitudinal
In the longitudinal direction ($z$), the interplay between acceleration, $ a = e E_{DC}/m $, in the DC gun and the physics of the photoemission process determine the properties of the electron bunch.
Two limiting regimes for the initial longitudinal variances $ \sigma_{i} ( 0 ) $ are readily identified: (i) by the incident drive laser pulse duration is sufficently long to ensure that the distance the electrons travel due to acceleration in $ E_{DC} $ over the laser pulse duration is much greater than that traveled by electrons with the maximum photoemission velocity $ v_{0} $ alone over the same time period; and (ii) the opposite regime for sufficiently short laser pulse durations.

@@

%v0 dominated
In the short pulse limit, where the acceleration in the DC gun field over the incident laser pulse duration can be neglected, the initial electron bunch properties are determined primarily by the photoemission physics.
%TODO describe new model
Careful analysis of the electron generation using the longitudinal $ v^{3} $ photoemission velocity distribution (Appendix \ref{sec:step_model}) and iterative time steps through the incident laser pulse reveals that, although the spatial electron bunch distribution is slightly skewed with respect to the symmetric incident laser pulse, its initial variance $ \sqrt{ \sigma_{ z } ( 0 ) } $ (or width) is nearly equal to that of the laser pulse of the normalization by the velocity ratio $ v_{ 0 }/c $; in other words,
\begin{equation} \label{eq:initial_sigma_z}
\sqrt{ \sigma_{ z } ( 0 ) } = v_{ 0 } \Delta t_{L} = \frac{ v_{ 0 } \tau }{ \sqrt{ 2 } } \, \text{.}
\end{equation}
Not unexpectedly, the analysis also indicates that the initial electron bunch has a velocity chirp.
%TODO description again
Its value is only roughly 6\% of $ v_{ 0 }/\sqrt{ \sigma_{z} ( 0 ) } $ since the photoemission generates the $ v^{ 3 } $ velocity distribution throughout the laser pulse; thus 
\begin{equation}
\gamma_{ z } ( 0 ) = m \sigma_{ z } ( 0 ) \frac{ d v }{ d z } \approx 0.06 m v_{ 0 } \sqrt{ \sigma_{ z } ( 0 ) } \, ,
\end{equation}
in this regime.
Additionally the iterative time-step analysis clearly shows that the local longitudinal momentum variance $ \eta_{ z } $ is not constant over the inital photo-generated electron bunch.
In fact, $ \sqrt{ \eta_{ z } ( 0 ) } $ varies by almost an order of magnitude over the $ 1/e^{2} $ maximum full-width of the electron bunch with the narrowest momentum distribution at the front of the bunch where only the faster electrons with velocity near $ v_{ 0 } $ initially reside.
Unfortunately, the mean-field theory of Michalik and Sipe \cite{michalik_analytic_2006} is not equipped to handle such a variation as it assumes a constant $ \eta_{ z } $ over the electron bunch.
Consequently, we will assume that $ \eta_{ z } $ is a constant over the bunch with a value given by $ \eta_{\smallT } ( 0 ) \cong 3.85 \eta{ z } ( 0 ) $ (see Appendix \ref{sec:step_model}): indeed in this short pulse regime, one can show that over the central $ \sim 75 \% $ of the electrons in the inital photo-generated bunch the variation in $ \sqrt{ \eta_{ z } ( 0 ) } $ is only about $ \pm 25 \% $.

These initial conditions at $t=0$ for an incident Gaussian laser pulse of the form given in \ref{eq:laser_form}, will be used for the remainder of this paper.
\begin{subequations} \label{eq:summary}
  \begin{gather}
    \sigma_{ \smallT } ( 0 ) = \frac{ w^{ 2 } }{ 2 } \\
    \sigma_{ z } ( 0 ) = \frac{ ( v_{ 0 } \tau )^{ 2 } }{ 2 } + \left ( \frac{ e E_{ DC } \tau^{ 2 } }{ 4 m } \right )^{ 2 } \\
    \gamma_{ \smallT } ( 0 ) = 0 \\
    \gamma_{ z } ( 0 ) = \sqrt{ \sigma_{ z } ( 0 ) } \left ( 0.06 m v_{ 0 } + \frac{ e E_{DC} \tau }{ \sqrt{ 2 } } \right ) \\
    \eta_{ \smallT } ( 0 ) = \frac{ m \epsilon_{ F } ( \hbar \omega - \Phi ) }{ 3 ( \hbar \omega + \epsilon_{ F } ) } \\
    \eta_{ z } ( 0 ) = \frac{ \eta_{ \smallT } ( 0 ) }{ 3.85 }
  \end{gather}
\end{subequations}
